---
title: "nmer_OriginalHomeworkCode_01"
author: "Nicole Merullo"
date: "2023-09-14"
output: 
  html_document:
    theme: yeti
    highlight: NULL
---

```{r setup, include=FALSE}
require(stringr)
```

## Challenge 1

```{r Challenge1, echo=TRUE}
u <- c("stately", "plump", "buck", "mulligan", "came", "from", "the", "stairhead", "bearing", "a", "bowl", "of", "lather", "on", "which", "a", "mirror", "and", "a", "razor", "lay", "crossed")
u
u[seq(from = 1, to = 22, by = 3)]
```

Trying again with the str_split() command
leaving the pattern argument blank (just closed quotation marks) would break it up by character, adding the space broke it up by word. 

```{r Challenge1 take 2, echo=TRUE}
u <- c("Stately plump Buck Mulligan came from the stairhead bearing a bowl of lather on which a mirror and a razor lay crossed")
u
u <- str_split_1(u, " ")
u[seq(from = 1, to = 22, by = 3)]
```

## Challenge 2

```{r Challenge2, echo=TRUE}
m <- matrix(data = 1:80, nrow = 8, ncol = 10, byrow = FALSE)
m
```

### extracting 2nd, 3rd, and 6th columns 

```{r Challenge2 part 1, echo=TRUE}
x <- c(m[, 2], m[, 3], m[, 6])
x
```

### extracting 6th to 8th rows

```{r Challenge2 part 2, echo=TRUE}
x <- c(m[6, ], m[7, ], m[8, ])
x
```

### extracting the elements from row 2, column 2 to row 6, column 9

```{r Challenge2 part 3, echo=TRUE}
x <- c(m[2, ], m[, 2:6], m[, 9])
x
```

## Challenge 3
Create a 4-dimensional 400 element array (5x5x4x4) named a consisting of numbers 400 to 1 (descending)
Subsetting this array requires 4 coordinates. Each one corresponds to a location/dimension. It's easiest to work backwards so the farthest right dimension working left to figure out how it gets a result. When a dimension is missing, it results any of the 4 options. 

```{r Challenge3, echo=TRUE}
a <- array(data = 400:1, dim = c(5, 5, 4, 4))
a
a[1, 1, 1, 2]
a[2, 3, 2, ]
a[1:5, 1:5, 3, 3]
```

## Challenge 4
Create lists within lists to reconstruct a primate phylogeny

```{r Challenge 5, echo=TRUE}
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Strepsirhini
Tarsioidea <- c("Tarsiidae")
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
Primates <- list(Haplorhini, Strepsirhini)
names(Primates) <- list("Haplorhini", "Stepsirhini")
Primates
```

## Challenge 5
Store the following numbers as a 5 x 3 matrix, called “m3”: 3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2. Be sure to fill the matrix ROW-WISE.

```{r Challenge 5, echo-TRUE}
m3 <- matrix(data = c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow = 5, ncol = 3, byrow = TRUE)
m3
```

Coerce from Matrix to Data Frame

```{r Challenge 5-2, echo-TRUE}
m3 <- as.data.frame(m3)
m3
```

Coerce the second column to be logic-valued

```{r Challenge 5-3, echo-TRUE}
m3 [, 2] <- as.logical(m3[, 2])
m3
```

Coerce the third column to be factor valued

```{r Challenge 5-4, echo-TRUE}
m3 [, 3] <- as.factor(m3[, 3])
m3
```

Use structure to see the data type for each variable (column)

```{r Challenge 5-5, echo-TRUE}
str(m3)
```